Some title

### 2018-01-13 tex/paper.tex
Paper

%\usepackage{todonotes}
\usepackage{svg}

@@

To this end we use an Artifical Neural Network based approach that can be initialized with a previously trained neural network or with random weights (without any preknowledge). When being used without any preknowledge the approach converges to a stable solution within the order of minutes and then outperforms existing congestion control algorithms with respect to throughput.

>>>>

%\usepackage{todonotes}
\usepackage{graphicx}
\graphicspath{figures}
\usepackage{svg}

@@

To this end we use an Artificial Neural Network based approach that can be initialized with a previously trained neural network or with random weights (without any preknowledge). When being used without any preknowledge the approach converges to a stable solution within the order of minutes and then outperforms existing congestion control algorithms with respect to throughput.

As in case of congestion control feedback used for reinforcement learning is naturally always delayed (due to the round trip time), we propose a novel approach to reinforcement learning that can handle delayed rewards as well as rewards that are returned in parts one after another.
